Grand Prix motorcycle racing

### 2020-08-03 inst/moto.Rmd
use cache

Each row is a driver (rider?) and each column (after the first) a
venue.  Takin the first row we see that Marquez came second in Qatar,
first in Argentina, retired in Austin, and so on.  In the first
column, we see the result from Qatar (QAT) in which Marquez came
second, Dovizioso first, Vinales third, and so on.  Notation used also
includes six different classes of no-score such as "Ret" for retired,
"WD" for withdrawn, and so on.  I now use bespoke R function
\code{ordertable2supp()}, that translates data of this type into a
log-likelihood.  The function is similar to, but slightly different
from, the analysis in `eurovision.R`.

@@

```{r,maxp2017}
options(width = 100)
m <- maxp(motoGP_2019)
m
dotchart(m,pch=16)
pie(m)
```

>>>>

Each row is a driver (rider?) and each column (after the first) a
venue.  Taking the first row we see that Marquez came second in Qatar,
first in Argentina, retired in Austin, and so on.  In the first
column, we see the result from Qatar (QAT) in which Marquez came
second, Dovizioso first, Vinales third, and so on.  Notation used also
includes six different classes of no-score such as "Ret" for retired,
"WD" for withdrawn, and so on.  I now use bespoke R function
\code{ordertable2supp()}, that translates data of this type into a
log-likelihood.  The function is similar to, but slightly different
from, the analysis in `eurovision.R`.

@@

```{r,maxp2017,cache=TRUE}
options(width = 100)
m <- maxp(motoGP_2019)
m
dotchart(m,pch=16)
pie(m)
```
